HW 2: Energy Demand and CO2 Emissions

### 2022-12-03 HW2/HW2.Rmd
finish hw2
fix hw 2.1-2.2

```{r}
hdvfe <- hdv1 %>% 
	filter(ITEM == "Average miles traveled per  gallon of fuel consumed") %>% 
	select(YEAR, `ALL HDV`) %>% 
	transmute(Year = YEAR, "Fuel economy (mpg)" = `ALL HDV`)

hdvfe %>% 
	kbl(booktabs = TRUE, caption = "Average Fuel Economy of HDVs") %>% 
	kable_styling(latex_options = "HOLD_position")
```

@@

```{r}
hdvem <- hdvfe %>% 
	mutate("Fuel consumption (gpm)" = 1/`Fuel economy (mpg)`,
				 "Emissions (g CO$_2$/gal)" = co2gal["diesel"],
				 "Emissions (g CO$_2$/mile)" =
				 	`Fuel consumption (gpm)` * `Emissions (g CO$_2$/gal)`)

@@

oldpower <- sum(tp$energy, na.rm = TRUE)
newpower <- oldpower - (regen/2)
```

@@

## 2.7
Low-sulfur diesel has an energy content of 128,488 Btu/gal according to the AFDC. This is equivalent to `r (energy <- 37.656)` kWh/gal. Assuming an engine efficiency of `r (eff <- 0.3)`, the total fuel needed for this drive cycle is $F = \frac{`r (oldpower) %>% round()`[\text{kWh}]/`r eff`}{`r energy %>% round(1)`[\text{kWh/gal}]} = `r (fuel1 <- oldpower/energy/eff) %>% round()`\ \text{gal}$. The total distance in this drive cycle is `r (totdist <- sum(tp$dist, na.rm = TRUE)) %>% round()` meters or `r (miles <- (totdist * .0006213712)) %>% round(1)` miles, giving an overall fuel economy of `r (miles/fuel1) %>% round(2)` mpg, and a fuel consumption of `r (fuel1/miles*1000) %>% round()` gallons per 1000 miles.

@@

@@

>>>>

```{r}
hdvfe <- hdv1 %>% 
	filter(str_detect(ITEM, "Fuel consumed") | str_detect(ITEM, "Total Rural and Urban")
	) %>% 
	select(YEAR, ITEM, `ALL HDV`) %>% 
	pivot_wider(names_from = ITEM, values_from = `ALL HDV`) %>% 
	`names<-`(c("Year", "Mmiles", "KgalFuel")) %>% 
	transmute(Year,
						"Fuel Economy (mpg)" = Mmiles*1000000 / (KgalFuel*1000))

hdvfe %>% 
	kbl(booktabs = TRUE, caption = "Average Fuel Economy of HDVs", digits = 1) %>% 
	kable_styling(latex_options = "HOLD_position")
```

@@

```{r}
hdvem <- hdvfe %>% 
	mutate("Fuel consumption (gpm)" = 1/`Fuel Economy (mpg)`,
				 "Emissions (g CO$_2$/gal)" = co2gal["diesel"],
				 "Emissions (g CO$_2$/mile)" =
				 	`Fuel consumption (gpm)` * `Emissions (g CO$_2$/gal)`)

@@

oldpower <- sum(tp$energy, na.rm = TRUE)
newpower <- oldpower - (regen/2)

enginepower <- sum(tp$`Engine Power (kW)`)
```

@@

## 2.7
Low-sulfur diesel has an energy content of 128,488 Btu/gal according to the AFDC. This is equivalent to `r (energy <- 37.656)` kWh/gal. Assuming an engine efficiency of `r (eff <- 0.3)`, the total fuel needed for this drive cycle is $F = \frac{`r (enginepower) %>% round()`[\text{kWh}]/`r eff`}{`r energy %>% round(1)`[\text{kWh/gal}]} = `r (fuel1 <- enginepower/energy/eff) %>% round()`\ \text{gal}$. The total distance in this drive cycle is `r (totdist <- sum(tp$dist, na.rm = TRUE)) %>% round()` meters or `r (miles <- (totdist * .0006213712)) %>% round(1)` miles, giving an overall fuel economy of `r (miles/fuel1) %>% round(2)` mpg, and a fuel consumption of `r (fuel1/miles*1000) %>% round()` gallons per 1000 miles.

@@

## 2.9

There are multiple possible reasons that hybrid vehicle technology is not more widely used in drayage trucks. Notably, drayage trucks are often old long-haul trucks, so vehicle purchases are not often made with drayage operation in mind. As such, trucks are purchased to be a good fit for long-haul operation, and since long-haul trucks need a large range and are usually at high speeds, hybrid technology becomes less efficient and less practical for this purpose. It also takes a long time to recoup fuel costs, and trucks are usually not owned long enough for that to be a financial incentive.

@@

## 3.3
Some notable sources of related emissions not included in the previous calculations are: vehicle production, transporting vehicles to dealerships or similar, refining of crude oil into gasoline, and mining operations needed for coal/natural gas.
